### 2025-10-23 src/articles/article11.qmd
Fix typos and formatting across the repo, Closes #5 (#6)
* fix ibl typo in article 3

* fix cwru typo article 8

* remove redundant backslashes

* fix appendix references

* fix labeling

   a. When an event is declared an {{< var glossary.official-chapter-event >}} by Executive Council ({{< var acronyms.ec >}}), all members must {{< var glossary.attend >}} it unless excused by {{< var acronyms.ec >}}. A missed {{< var glossary.official-chapter-event >}} that is not excused will count as an unexcused mandatory event.
      i. Missing a mandatory event without an accepted excuse will count as unexcused.
      i. A brother who has three unexcused mandatory events in a row must be brought up for standards by the Secretary with the possibility of recommendation for suspension.\
      i. A brother who has three unexcused mandatory events throughout the semester will be {{< var glossary.staggard >}}.
      i. A brother who has four unexcused mandatory events throughout the semester will be placed on probation until the end of the semester.
      i. A brother who has seven or more unexcused mandatory events throughout the semester will be brought up for standards by the secretary with the possibility of recommendation for suspension.

>>>>

   a. When an event is declared an {{< var glossary.official-chapter-event >}} by Executive Council ({{< var acronyms.ec >}}), all members must {{< var glossary.attend >}} it unless excused by {{< var acronyms.ec >}}. A missed {{< var glossary.official-chapter-event >}} that is not excused will count as an unexcused mandatory event.
      i. Missing a mandatory event without an accepted excuse will count as unexcused.
      i. A brother who has three unexcused mandatory events in a row must be brought up for standards by the Secretary with the possibility of recommendation for suspension.
      i. A brother who has three unexcused mandatory events throughout the semester will be {{< var glossary.staggard >}}.
      i. A brother who has four unexcused mandatory events throughout the semester will be placed on probation until the end of the semester.
      i. A brother who has seven or more unexcused mandatory events throughout the semester will be brought up for standards by the secretary with the possibility of recommendation for suspension.

### 2025-10-23 src/articles/article3.qmd
Fix typos and formatting across the repo, Closes #5 (#6)
* fix ibl typo in article 3

* fix cwru typo article 8

* remove redundant backslashes

* fix appendix references

* fix labeling

1. A brother who has three unexcused absences in a row must be brought up for standards by the Secretary in accordance with Article V, Section 2, Item j.1 of the IBL.
1. A brother who has three unexcused absences throughout the semester will be {{< var glossary.staggard >}}.
1. A brother who has four unexcused absences throughout the semester will be placed on {{< var glossary.probation >}} until the end of the semester.
1. A brother who has seven unexcused absences throughout the semester will be brought up for standards by the Secretary with the possibility of suspension.

>>>>

1. A brother who has three unexcused absences in a row must be brought up for standards by the Secretary in accordance with Article V, Section 2, Item j.1 of the {{< var acronyms.ibl >}}.
1. A brother who has three unexcused absences throughout the semester will be {{< var glossary.staggard >}}.
1. A brother who has four unexcused absences throughout the semester will be placed on {{< var glossary.probation >}} until the end of the semester.
1. A brother who has seven unexcused absences throughout the semester will be brought up for standards by the Secretary with the possibility of suspension.
